\documentclass[..\manual.tex]{subfiles}

\begin{document}
The GUI at its core is a chromium web instant. At the top right is a button that can be used to access the back-end connection management windows where the user can start an instant of the Python back-end and manually adding more server connections to split user's the workload.\par

\section{User Input}
The GUI accepts protein sequences in FASTA format either in raw text or a text file. The user can perform in-silico trypsin digestion of the input with optional ability to manually or automatically select sites for misdigestion.

\subsection{Modification Customization}
Within user settings tab, the user can use their own table of modifications as modifications source for the program. The table is made up of 10 columns where,
\begin{itemize}
    \item \textbf{name} is the name of the modification to be displayed on the GUI.
    \item \textbf{label} is the internal label of the modification to be used by the back-end. Must be in lowercase. No modifications within the same query should have the same label beside transition of the same Ytype variable modification.
    \item \textbf{mass} is the mass of the modification.
    \item \textbf{regex} is the regular expression representation of the the modification.
    \item \textbf{type} is the modification type \emph{Ytype}, \emph{variable}, or \emph{static}.
    \item \textbf{Ytype} is the label of the Ytype transition.
    \item \textbf{multiplepattern} is whether the query with this variable modification is default to have all modification pattern generated.
    \item \textbf{status} is whether the query with this variable modification is default to be filled in every instance on the sequence.
\end{itemize}
\begin{table}
	\caption{Example of a user submitted modifications table}
	\begin{adjustbox}{width=1\textwidth}
		\small
		\begin{tabular}{c c c c c c c c c c}
			\hline name & label & mass & regex & type & Ytype & multiplepattern & status & mlabel & offset \\ [0.1ex]
			\hline\hline
			O-Mannose & g & 0 & [S$|$T] & Ytype & Y0 & false & false & & 0 \\
			O-Mannose & g & 162.05 & [S$|$T] & Ytype &  Y1 & false & false & & 0 \\
			HexNAc & h & 0 & N[\^{}P][S$|$T] & Ytype &  Y0 & false & false & & 2 \\
			Propionamide & c & 71.037114 & C & static &  & false & false & PPa & 0 \\
			Carboxylation & e & 43.98983 & E & variable &  & false & false &  & 0 \\
		\end{tabular}
	\end{adjustbox}
\end{table}

\subsection{SWATH Window Customization}

\end{document}